Differences in Homicide Case Information Indicates Why Justice is Not Served

### 2024-12-13 paper/paper.qmd
Updated overview

### Overview
@datahomicides compiled a dataset containing 52,179 homicides from the 50 largest cities in the United States. In this dataset, they gathered information about the homicide victim's first and last name, the date they were reported to be found (in YYYY/MM/DD format), the victim's race, the victim's age, the victim's sex, the city and the state the homicide took place in, the longitude and latitude of the homicide location, and disposition/status of the homicide [@datahomicides]. The dataset was eventually used in @citewashingtonpostmap to map location of homicides and analyze arrest rates across the different cities. We will be evaluating @datahomicides's methodology by looking at their sampling approach and evaluating the strengths and weaknesses of their methodology.

>>>>

### Overview
@datahomicides compiled a dataset containing 52,179 homicides from the 50 largest cities in the United States. In this dataset, they gathered information about the homicide victim's first and last name, the date they were reported to be found (in YYYY/MM/DD format), the victim's race (Eg. White, Hispanic, Black, Asian, Other, Unknown), the victim's age, the victim's sex (Eg. Female, Male, Unknown), the city and the state the homicide took place in, the longitude and latitude of the homicide location, and disposition/status of the homicide [@datahomicides]. The dataset was eventually used in @citewashingtonpostmap to map location of homicides and analyze arrest rates across the different cities. We will be evaluating @datahomicides's methodology by looking at their sampling approach and evaluating the strengths and weaknesses of their methodology.
